\NAME: A framework for \\ Efficient Intrusion Detection\\ in the Internet of Things

### 2014-10-22 paper.tex
minor changes to the original evaluation text

Tables \ref{tbl:manual} and \ref{tbl:generated} show the collected data
respectively for the manual and the generated implementation. The base case is
presented in absolute values, while the implementations with the added
algorithms are presented as relative values.

@@

When comparing the results of both implementations we first can conclude that
the generator produces exactly the same code for the base case. We couldn't
measure any real differences between both implementations.

>>>>

Tables \ref{tbl:manual} and \ref{tbl:generated} show the collected data
respectively for the manual and the generated implementation. The base case is
presented in absolute values, while the implementations with the ID algorithms
added are presented as relative values.

@@

When comparing the results of both implementations we first can conclude that
the generator produces exactly the same code for the base case. We couldn't
measure any real differences between both implementations. It's important to
validate this aspect to ensure that both implementations are structurally
comparable.
